Main Analysis

### 2024-12-17 Manuscript Analysis/main_analysis.Rmd
updated figures

The purpose of this document is to analyze and report findings related to M. Hirsch's dissertation project. The data preparation and analysis was conducted using R Version 4.3.3.

@@

ple_data |>
  dplyr::group_by(speaker, rep_acc) |>
  dplyr::summarize(per_effort = mean(effort_rating, na.rm = T), 
                   sd = sd(effort_rating, na.rm = T),
                   se = sd/sqrt(n())) |>
  ggplot() +
   aes(x = rep_acc,
       y = per_effort,
       group = speaker,
       color = speaker,
       fill = speaker) +
  geom_bar(stat = "identity", alpha = 0.6, position = position_dodge()) +
  geom_errorbar(aes(ymin = per_effort - se, ymax = per_effort + se), width = 0.4, position = position_dodge(.9)) +
  labs(x = "Accuracy", y = "Perceived Listening Effort Rating", color = "Speaker", fill = "Speaker") +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_color_manual(values = c(my_pal[1], my_pal[5]), labels =  c("Neurotypical", "ALS")) +
  scale_fill_manual(values = c(my_pal[1], my_pal[5]), labels = c("Neurotypical", "ALS"))

@@

Adding in AR(1) structure to address autocorrelation concerns. Bumped up knots to 25.

>>>>

The purpose of this document is to analyze and report findings related to M. Hirsch's dissertation project. The results from this analysis were also used to prepare for publication.

The data preparation and analysis was conducted using R Version 4.4.1.

@@

ple_data |>
  dplyr::group_by(speaker, rep_acc) |>
  dplyr::summarize(per_effort = mean(effort_rating, na.rm = T), 
                   sd = sd(effort_rating, na.rm = T),
                   se = sd/sqrt(n())) |>
  ggplot() +
   aes(x = rep_acc,
       y = per_effort,
       group = speaker,
       color = speaker,
       fill = speaker) +
  geom_bar(stat = "identity", alpha = 0.6, position = position_dodge()) +
  geom_errorbar(aes(ymin = per_effort - se, ymax = per_effort + se), width = 0.4, position = position_dodge(.9)) +
  labs(x = "Accuracy", y = "Perceived Listening Effort Rating", color = "Speaker", fill = "Speaker") +
  theme_bw() +
  theme(aspect.ratio = 1,
        legend.position = "bottom") +
  scale_color_manual(values = c(my_pal[1], my_pal[5]), labels =  c("Neurotypical", "ALS")) +
  scale_fill_manual(values = c(my_pal[1], my_pal[5]), labels = c("Neurotypical", "ALS"))

@@

Adding in AR(1) structure to address autocorrelation concerns.
